### 2019-12-09 README.Rmd
Minor fix (proposal) on string 70 (#281)

Here we show a the creation of a relatively complete EML document using `EML`.  This closely parallels the function calls shown in the original EML [R-package vignette](https://ropensci.github.io/EML/articles/creating-EML.html).

>>>>

Here we show the creation of a relatively complete EML document using `EML`.  This closely parallels the function calls shown in the original EML [R-package vignette](https://docs.ropensci.org/EML/articles/creating-EML.html).
